Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-09 ms.tex
define SSPP acronym and cite SSPP reference

We calibrate optical depth to reddening empirically rather than derive a 
relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution. To achieve this
empirical calibration, we must adopt a set of calibrator objects for which true
optical reddening is known. There are various possibilities at our disposal. 
\cite{planckdust} calibrated their radiance and $\tau_{353}$ maps to $E(B-V)$ 
using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} photometry for a
set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
sample of 384 elliptical galaxies, but was later revised by 
\citet[hereafter SF11]{schlafly11} based on $\sim$260,000 stars with both 
spectroscopy and broadband photometry available from SDSS.

@@

\subsection{Rectifying Reddening Residuals}
In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).

>>>>

We calibrate optical depth to reddening empirically rather than derive a 
relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution. To achieve this
empirical calibration, we must adopt a set of calibrator objects for which true
optical reddening is known. There are various possibilities at our disposal. 
\cite{planckdust} calibrated their radiance and $\tau_{353}$ maps to $E(B-V)$ 
using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} photometry for a
set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
sample of 384 elliptical galaxies, but was later revised by 
\citet[hereafter SF11]{schlafly11} based on $\sim$260,000 stars with both 
spectroscopy and broadband photometry available from the SEGUE Stellar 
Parameter Pipeline \citep[SSPP,][]{sspp}.

@@

\subsection{Rectifying the Reddening Residuals}
In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).
